\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2025-05-30 manuscript/reply.tex
response to opening summaries of AE and reviewers

\begin{comment}

Two reviewers have carefully read the paper and have provided detailed feedback.  Both reviewers would like to see some additional discussion and justifications for the bias correction term, where one could closely follow the Babu and Rao (2004) paper, and one reviewer mentioned the importance of considering different block sizes (I recommend possibly trying some data-based block size selection method and checking how it performs).  A successful revision will require that the authors give serious consideration to these points.
\end{comment}

@@

Thank you for pointing out this error in our manuscript. We have corrected
it from "nonparametric" to "parametric" accordingly.

@@

@@

@@

Thank you for pointing this out. In the second paragraph of Section 3.1, 
we have added that the
serial dependence is specifically between $X_i$ and $X_{i+1}$.

>>>>

\begin{comment}
Two reviewers have carefully read the paper and have provided detailed feedback.  Both reviewers would like to see some additional discussion and justifications for the bias correction term, where one could closely follow the Babu and Rao (2004) paper, and one reviewer mentioned the importance of considering different block sizes (I recommend possibly trying some data-based block size selection method and checking how it performs).  A successful revision will require that the authors give serious consideration to these points.
\end{comment}

We thank the AE for the careful reading and encouraging feedback. The
reviewers’ comments have been addressed to the best of our ability in
the revised manuscript. We have added a heuristic justification for
the bias correction term in Section~2.4, following the logic of
\citet{babu2004goodness}, and clarified its extension to the block
bootstrap setting. As suggested, we also implemented a data-driven
block size selection method based on \citet{politis2004automatic} and
evaluated its performance. The results are included in the Appendix,
along with a discussion of the challenges posed by automatic block
length selection under strong serial dependence. Please find our
detailed point-by-point responses below.

@@

Fixed.

\jy{Is there a second point from the AE?}

@@

We thank the reviewer for the thoughtful comments and for recognizing
the clarity of the manuscript. While the methodological foundation
builds on existing work, the extension of the bias-corrected
nonparametric bootstrap of \citet{babu2004goodness} to stationary time
series with unspecified serial dependence is, to our knowledge, new
and practically valuable. As the reviewer noted, the paper targets a
general audience; accordingly, we added for a heuristic justification
of the bias correction term in Section~2.4 and clarified how the
approach adapts and differs from the i.i.d. setting in the presence of
serial dependence. We have revised the Introduction and Discussion
sections to better emphasize the scope and contribution.

@@

We thank the reviewer for their accurate and concise summary of our
contribution.

@@

Thank you for pointing this out. In the second paragraph of
Section~3.1, we have added that the serial dependence is specifically
between $X_t$ and $X_{t+1}$.
